Notes on \\ Projected Knowledge Compilation \\ \today

### 2023-08-08 doc/pkc-notes.tex
Fix detail on partitioning

\newcommand{\simplify}[2]{#1|_{#2}}
\newcommand{\ureduce}[2]{\forall #2\, #1}
\newcommand{\partition}[2]{\mathit{Part}(#1, #2)}

@@

\newcommand{\algo}[1]{\textsf{#1}}
\newcommand{\kc}{\algo{KC}}
\newcommand{\pkc}{\algo{PKC}}
\newcommand{\traverse}{\algo{Traverse}}
\newcommand{\cfilter}{\algo{FilterClause}}
\newcommand{\lfilter}{\algo{FilterLiteral}}
\newcommand{\bcp}{\algo{BCP}}
\newcommand{\uprop}{\algo{Uprop}}
\newcommand{\simpl}{\also{Simpl}}

@@

\item[$\partition{\phi}{Y}$:] Find the subset of clauses that depend only on the variables in $Y$:
$\partition{\phi}{Y} = \{ C \in \phi \mid \dependencyset(C) \subseteq Y\}$.

@@

\item[Literals:]
  $\traverse(\lit, \phi) = \lit$ if $\dependencyset(\lit) \subseteq \dvarset$, and $\traverse(\lit, \phi) = \tautology$ if $\dependencyset(\lit) \in \pvarset$.
\item[Product Operations:]
  Let the operation be of the form $P(\lit_1, \lit_2, \ldots, \lit_k, \psi_1, \psi_2, \ldots, \psi_m)$, where each $\psi_i$ is either a sum or a  product operation.
  \begin{enumerate}
  \item Let $L = \{\lit_1, \lit_2, \ldots, \lit_k\}$.
  \item Define clausal formula $\phi'$ to be $\bcp(\simplify{\phi}{L})$
  \item For $1 \leq i \leq m$, recursively compute $\psi'_i = \traverse(\psi_i, \partition{\phi'}{\dependencyset(\psi_i)})$.  (Partitioning is only required when $m > 1$.)
  \item Return the product (with simplifications) for the set of arguments $\{\lit \in L \mid  \dependencyset(\lit) \subseteq \dvarset\} \cup \{ \psi'_i \mid  1 \leq i \leq m \}$.
  \end{enumerate}
\item[Sum Operations:]
  Let the operation be of the form $S(\lit_1, \lit_2)$ and having decision variable $x$.
  \begin{enumerate}
  \item For $1 \leq i \leq 2$, recursively compute $\psi'_i = \traverse(\psi_i, \phi)$.
  \item If $x \in \dvarset$, then return the sum (with simplifications) $S(\psi'_1, \psi'_2)$.
  \item Otherwise, let $\psi_{\forall} = \pkc(\ureduce{\phi}{x})$
    \begin{enumerate}
    \item If $\psi_{\forall} = \nil$, then return the sum (with simplifications) $S(\psi_1, \psi_2)$
    \item Otherwise return nested formula $S(\neg S(\neg \psi'_1, \psi_{\forall}), \psi'_2)$.
    \end{enumerate}
  \end{enumerate}
\end{description}

>>>>

\newcommand{\simplify}[2]{#1|_{#2}}
\newcommand{\ureduce}[2]{\forall #2\, #1}

@@

\newcommand{\algo}[1]{\textsf{#1}}
\newcommand{\kc}{\algo{KC}}
\newcommand{\pkc}{\algo{PKC}}
\newcommand{\traverse}{\algo{Traverse}}
\newcommand{\cfilter}{\algo{FilterClause}}
\newcommand{\lfilter}{\algo{FilterLiteral}}
\newcommand{\bcp}{\algo{BCP}}
\newcommand{\uprop}{\algo{Uprop}}
\newcommand{\partition}{\algo{Partition}}
\newcommand{\occur}{\algo{Occur}}

@@

\item[$\occur(\phi, Y)$:] Iteratively expand the set of variables $Y$ to include all those variables that co-occur in one or more clauses in $\phi$.
  That is, starting with $Y' = Y$,
  repeatedly compute $Y' \leftarrow Y' \cup \dependencyset(C)$
  for every clause $C$ such that $Y' \cap \dependencyset(C) \not = \emptyset$,
  until a fixed point is reached, and then return $Y'$.

\item[$\partition(\phi, Y)$:] Find the subset of clauses that depend only on the variables in $\occur(Y)$:
$\partition(\phi, Y) = \{ C \in \phi \mid \dependencyset(C) \subseteq \occur(Y)\}$.

@@

\item[Literals:]
  $\traverse(\lit, \phi) = \lit$ if $\dependencyset(\lit) \subseteq \dvarset$, and $\traverse(\lit, \phi) = \tautology$ if $\dependencyset(\lit) \in \pvarset$.
\item[Product Operations:]
  Let the operation be of the form $P(\lit_1, \lit_2, \ldots, \lit_k, \psi_1, \psi_2, \ldots, \psi_m)$, where each $\psi_i$ is either a sum or a  product operation.
  \begin{enumerate}
  \item Let $L = \{\lit_1, \lit_2, \ldots, \lit_k\}$.
  \item Define clausal formula $\phi'$ to be $\bcp(\simplify{\phi}{L})$
  \item For $1 \leq i \leq m$, recursively compute $\psi'_i = \traverse(\psi_i, \partition(\phi', \dependencyset(\psi_i)))$.  (Partitioning is only required when $m > 1$.)
  \item Return the product (with simplifications) for the set of arguments $\{\lit \in L \mid  \dependencyset(\lit) \subseteq \dvarset\} \cup \{ \psi'_i \mid  1 \leq i \leq m \}$.
  \end{enumerate}
\item[Sum Operations:]
  Let the operation be of the form $S(\lit_1, \lit_2)$ and having decision variable $x$.
  \begin{enumerate}
  \item For $1 \leq i \leq 2$, recursively compute $\psi'_i = \traverse(\psi_i, \phi)$.
  \item If $x \in \dvarset$, then return the sum (with simplifications) $S(\psi'_1, \psi'_2)$.
  \item Otherwise, let $\psi_{\forall} = \pkc(\ureduce{\phi}{x})$
    \begin{enumerate}
    \item If $\psi_{\forall} = \nil$, then return the sum (with simplifications) $S(\psi_1, \psi_2)$
    \item Otherwise return nested formula $S(\neg S(\neg \psi'_1, \psi_{\forall}), \psi'_2)$.
    \end{enumerate}
  \end{enumerate}
\end{description}
